AttCRISPR : an spacetime interpretable model for on-target activity of sgRNA prediction

### 2020-11-02 Paper/main.tex
11-2 paper

\title[short Title]{AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction
}
\author[Sample \textit{et~al}.]{Corresponding Author\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

>>>>

\title[short Title]{AttCRISPR : an spacetime interpretable model for on-target activity of sgRNA prediction
}
\author[Xiao \textit{et~al}.]{Liming Xiao\,$^{\text{\sfb 1}}$, Yunqi Wan\,$^{\text{\sfb 1}}$ and Zhenran Jiang\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Department of Computer Science \& Technology, East China Normal University, Shanghai, 200062, China.}
